Glyph-maps for visualizing climate data and models

### 2011-09-01 paper.tex
polar coordinates: more detailed explanation & example

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{euclid-to-polar-1}%
  \includegraphics[width=0.5\linewidth]{euclid-to-polar-2}

  \caption{Examples for some small time series with strongly expressed trends in Euclidean coordinates (left) and polar coordinates (right).}
  \label{fig:ref-basic-polar}
\end{figure}

Figure \ref{fig:ref-basic-polar} gives some small examples of time series with strongly expressed trends, shown both in cartesian coordinates and polar coordinates. What might be surprising is that time series that seem to have opposing trends in cartesian coordinates don't necessarily show this symmetry  in polar coordinates. What becomes apparent, though is that the area of glyphs in polar coordinates mainly reflect the average value of a time series, while its shape shows deviations from average values. Adding a circular reference line helps to pick out these deviations.
